\plaintitle

### 2017-01-11 drafts/labor/introduction.tex
cleaned up intro a bit

\topic{This body of research has broadly worked toward the answer to one central question:
\textit{What does the future hold for on--demand work and those who do it?}}
Researchers have offered insights on this question along three major threads:
First, \namerefl{sec:complexity} ---
specifically, how complex are the goals that crowd work can accomplish, and
what kinds of goals and industries may eventually utilize it~\cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364,crowdForgeKittur}?
Second, \namerefl{sec:decomposition}~\cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}?
And third, \namerefl{sec:relationships}~\cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}?

@@

>>>>

\topic{This body of research has broadly worked toward the answer to one central question:
\textit{What does the future hold for on--demand work and those who do it?}}
Researchers have offered insights on this question along three major threads:
First, \namerefl{sec:complexity} ---
specifically, how complex are the goals that crowd work can accomplish, and
what kinds of goals and industries may eventually utilize it~\cite{suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}?
Second, \namerefl{sec:decomposition}~\cite{sensitiveTasks,LykourentzouPersonalityMatters,Law:2016:CKC:2858036.2858144,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}?
And third, \namerefl{sec:relationships}~\cite{turkopticon,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}?

@@

\onlyinsubfile{
  \printbibliography
}
